### 2019-08-02 Thesis/pages/design.tex
Changes; - Small changes made to the main experiment - Updated lists of vuln keys - Added more content to the thesis

Near-collision keys are keys that are deemed a match by the phonetic similar metric (More on this aspect in the following sections). A similarity metric is an algorithm designed to determine if two words are phonetically a match. For example, the words "THEIR" and "THERE" will be phonetically be a match whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.

As each combined key in Trustwords is an exclusive-or of both sides public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is target to a single pair of users and will require recomputation for every attack instance, this will be considered when discussing the attack feasibility. Each pair is also split into a "Uncontrolled" and "Controlled" key. Uncontrolled is the reciever of the communication, and, thus, we cannot control their key. The Controlled key is the one we are attempting to impersonate, and it is assumed that we have the ability to replace the Controlled key with our malicious option. These descriptions will be the terminology used throughout the paper. However, it should also be considered that the uncontrolled and controlled can be swapped around with the ability to compute both directions. Thus, resulting in the possibility to intercept both directions of communication. This, however, will require performing the attack separately for both directions.

@@

Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and Metaphone 3 (2009) claim to improve over the original version due to further research performed by Philips. The original version was chosen due to its historical widespread usage.

@@

Phonetic features are used in this work as a way to compare the similarity of a words phonemes. Phonemes are the phonetic elements that construct a word. For example the word "RING" translated into the phonemes \verb|/R IH NG/|. Extensive prior work has gone into producing models of features that map to phonemes. \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}. Features, therefore, are an attempt at mapping the varying and inconsistent rules around pronunciation of the English language. The vectors are created using lists phonemes from the CMU Pronouncing Dictionary. Using all words available in the CMU Dictionary and mapping all phonemes to phonetic features produces a list of unique features.

@@

The first was the addition of 5 "Random matches" questions. These were two random words selected from the dictionary. Therefore, the overall rating of these words should be close to an average of 1. This allows a simple check to see if the user is providing valid results. If their average is too high, the results will also be discarded.

@@

\textbf{TODO: } Explain why the attacks are designed like this. Use heatmap study as justification as why the ends are prioritised.

>>>>

Near-collision keys are keys that are deemed a match by the phonetic similarity metric (More on this aspect in the following sections). A similarity metric is an algorithm designed to determine if two words are phonetically a match. For example, the words "THEIR" and "THERE" will be a match whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.

As each combined key in Trustwords is an exclusive-or of both sides public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is target to a single pair of users and will require recomputation for every attack target. This will be considered when discussing the attack feasibility. Each pair is also split into a "Uncontrolled" and "Controlled" key. Uncontrolled is the reciever of the communication, and, thus, we cannot control their key. The Controlled key is the one we are attempting to impersonate, and it is assumed that we have the ability to replace the Controlled key with our malicious option. These descriptions will be the terminology used throughout the paper. However, it should also be considered that the uncontrolled and controlled can be swapped around with the ability to compute both directions. Thus, resulting in the possibility to intercept both directions of communication. This, however, will require performing the attack separately for both directions.

@@

Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and Metaphone 3 (2009) that claim to improve over the original version due to further research performed by Philips. The original version was chosen due to its historical and widespread usage.

@@

Phonetic features are used in this work as a way to compare the similarity of a words phonemes. Phonemes are the phonetic elements that construct a word. For example the word "RING" translated into the phonemes \verb|/R IH NG/|.

Extensive prior work has gone into producing models of features that map to phonemes. \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}. Features, therefore, are an attempt at mapping the varying and inconsistent rules around pronunciation of the English language. The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.

@@

The first was the addition of 5 "Random matches" questions. These were two random words selected from the dictionary. Therefore, the overall rating of these words should be close to an average of 1. This allows a simple check to see if the user is providing valid results. If their average is too high, the results will be discarded.

@@

The start and ends were chosen as the highest priority words to keep static. This is due to research highlighting on the common habit of users to only check the start and end of a checksum. \cite{cherubini2018towards} shows this by measuring user eye movement and displaying it as a heat map.

\begin{figure}[h!]
    \centering
    \fbox{
        \parbox{\textwidth}{
            \includegraphics[width=\textwidth]{checksum_check.png}

            \includegraphics[width=\textwidth]{checksum_check_2.png}
        }
    }
    \caption{Failed verification of an incorrect checksum\cite{cherubini2018towards}}
    \label{fig:heatMap}
\end{figure}

Figure \ref{fig:heatMap} shows the results of a eye tracking experiment where the user failed to detect a mismatching digest. As it can be clearly seen the users never compared the center of the digest.

However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end. However, we believe that attention will also play a part in defining the most important areas of comparison as the hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end. All these aspects, however, will require empirical evidence to arrive at a conclusion. Therefore, this consideration will need to be made when assessing the results of the experiment.

### 2019-08-02 Thesis/pages/implementation.tex
Changes; - Small changes made to the main experiment - Updated lists of vuln keys - Added more content to the thesis

>>>>

\textbf{TODO: } Talk here about the interesting and challenges that were overcome

\section{GreenOnion}
Talk about the way a key is expanded and turned into a lot
of work for the kernel

\section{First Experiment}
Explain how Google App Script was used?

\section{MainExperiment}
Design of the application etc

### 2019-08-02 Thesis/pages/lit_review.tex
Changes; - Small changes made to the main experiment - Updated lists of vuln keys - Added more content to the thesis

\chapter{Literature Review}
\label{cha:LiteratureReview}

@@

\section{Public-key Cryptography and Key Exchange}
Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others. The use-case of E2EE messages will be the primary focus of this paper.

@@

\section*{Definition of terms}
Throughout the paper, various terms are used to define elements of the authentication ceremony relevant to fingerprints verification. Explicit descriptions are, therefore, stated in this section. These are used to remove ambiguity and underlying associations readers may have for the words chosen.
\\\\
\textbf{\textit{Encoding schemes}} - This is the physical method of encoding used to represent the fingerprint. For example, ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.
\\\\
\textbf{\textit{Method of comparison}} - This is how the user assesses the encoding scheme. The most common example and the one used as default is ``Compare-and-Confirm'' (CaC). CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}. The following sections explain alternative methods of comparisons.

\section{Authentication ceremony performance}

\section*{Encoding scheme performance}
Results 
from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}. In all cases, these were the best schemes from the sets assessed. The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\%.
\\\\
Aside from textual representations were graphical schemes. Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/}, among others. These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}. The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
\\
\begin{table}[h!]
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_times.tex}
    }%
    \caption{Timing results in seconds for the related schemes}
    \label{tab:times}
\end{table}
\\
In terms of usability of graphical schemes, the literature concurred on their high usability. The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings). Other work also indirectly concurred with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical}\cite{kainda2009usability}.
In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with literature only containing two papers. There is also no overlap in the schemes assessed with each paper reviewing a unique set. This is, therefore, a promising candidate for further research.

@@

\section*{Methods of comparison performance}
Aside 
from ``Compare-and-Confirm'' (CaC), there is ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE). CaS is the method where one device displays the fingerprint, and the other user is provided with several options. The user then has to choose the correct value from the list of candidates. If there is no match, the user must deny the connection attempt. The creation of CaS was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}. CaE is designed for scenarios where both devices might not have a display, i.e. pairing between a phone and a keyboard. One device displays the checksum. This checksum is entered into the other device. The first device then compares the entered string and checks for a match.

@@

\section*{Experimentation methodology comparison}
To further look into the validity of previously discussed results, it is necessary to asses how the respective studies reached these conclusions. Areas for consideration are scheme entropy, attacker strength and participant attributes.

@@

%TODO: Maybe talk about the effect of visual or mental impairments 
\subsection{Topic conclusion}
Overall, this review has identified several key areas suitable for further work.
The first is the performance assessment of graphical encoding schemes. Recreation of pre-existing results from \cite{hsiao2009study}\cite{tan2017can} is required to corroborate current conclusions and validate results.
Another gap in the research is the consideration into the utilization of encoding schemes in realistic conditions, i.e. ``remove vs. proximity." This topic was initially covered by \cite{shirvanian2017pitfalls} but their scope was limited. Further work, therefore, could increased the scope and touch upon a large number of schemes in these settings.
The final aspect for further work is the limited consideration into the feasibility of attacks on encoding schemes. All of the papers assessed simulated attacks and had minimal consideration for the execution of these attacks. Therefore, further work could delve into the implementation of such attacks and their feasibility in terms of compute and storage complexity.

\section{Encoding schemes}
Another area of research is investigations into the actual physical encodings of the hash digest. This section will briefly discuss the current research available on the creation and security of actual encoding schemes. The actual details of the operation of the schemes are outside the scope of this literature review, therefore, minimal attention will be allocated to these details.

@@

\subsubsection{Pretty Easy Privacy}
\label{sec:pep}
A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}. \pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email or SMS. The imbedded design principles state that above all the systems should be easy to install, use and understand.

@@

\subsection{Topic conclusion}

@@

\section{Attacks on encoding schemes}
This area of research studies ways to physically execute attacks on fingerprint encoding schemes. This differs from previously examined work due to papers discussing the performance and fallibility of encoding schemes simulated the attack without consideration for how the attack would be performed. Research in this area is scant, with lots of research attention being directed towards the security of Man-in-the-Middle (MITM) attacks and not the encoding schemes themselves.

@@

\subsection{Topic Conclusion}
Overall the literature for this subtopic remains sparse and incomplete. Further suggested work could look into the feasibility of generating partial collisions for all textual representations alongside quantified effectiveness on users. With the possibility to concentrate on a few selected implementations. The work would aim to focus on the various physical methods used and their feasibility. This is one area the previous literature has failed to cover and has only theoretically quantified attacker strength without consideration for the actual real-world cost of these attacks.

>>>>

\chapter{Background}
\label{cha:LiteratureReview}

@@

The chapter will contain the following sections:

\begin{itemize}
    \item \textbf{Project context} \\ 
    Will provide the user with the base knowledge required to understand the context and purpose of the following literature review.

    \item \textbf{Definition of terms}\\
    Specific definitions relevant to the literature review will initially be defined.

    \item \textbf{Literature Review} \\
    A review of currently available literature on relevant topics. Recommendations and research gaps will be identified and discussed.

\end{itemize}

\section{Project context}

\subsection*{Public-key Cryptography and Key Exchange}

To fully understand the literature review it is necessary to introduce and explain the base knowledge before continuing.

Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others. The use-case of E2EE messages will be the primary focus of this paper.

@@

\section{Definition of terms}
Throughout the paper, various terms are used to define elements of the authentication ceremony relevant to fingerprints verification. Explicit descriptions are, therefore, stated in this section. These are used to remove ambiguity and underlying associations readers may have for the words chosen.
\\\\
\textbf{\textit{Encoding schemes}} - This is the physical method of encoding used to represent the fingerprint. For example, ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.
\\\\
\textbf{\textit{Method of comparison}} - This is how the user assesses the encoding scheme. The most common example and the one used as default is ``Compare-and-Confirm'' (CaC). CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}. The following sections explain alternative methods of comparisons.

\section{Literature Review}
This section will now discuss the current research around the proposed topic.

The section is organized as follows:

\begin{itemize}
    \item \textbf{Authentication ceremony performance} \\
    This section explains the current research on performance of various encoding schemes and methods of comparison. This is then complemented with an assessment of the experimentation design for the respective studies.

    \item \textbf{Encoding schemes} \\
    The following section then discusses research around the design of an encoding scheme. Focus in this section will be allocated to the technical details around the creation and design of relevant schemes.

    \item \textbf{Attacks on encoding schemes} \\
    The final section will then discuss literature that investigates the creation of attacks against encoding schemes in order to deceive the respective users.
\end{itemize}

\subsection{Authentication ceremony performance}

\subsubsection*{Encoding scheme performance}
Results 
from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}. In all cases, these were the best schemes from the sets assessed. The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\%.
\\\\
Aside from textual representations were graphical schemes. Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/}, among others. These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}. The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
\\
\begin{table}[h!]
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_times.tex}
    }%
    \caption{Timing results in seconds for the related schemes}
    \label{tab:times}
\end{table}
\\
In terms of usability of graphical schemes, the literature concurred on their high usability. The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings). Other work also indirectly concurred with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical}\cite{kainda2009usability}.
In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with literature only containing two papers. There is also no overlap in the schemes assessed with each paper reviewing a unique set. This is, therefore, a promising candidate for further research.

@@

\subsubsection*{Methods of comparison performance}
Aside 
from ``Compare-and-Confirm'' (CaC), there is ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE). CaS is the method where one device displays the fingerprint, and the other user is provided with several options. The user then has to choose the correct value from the list of candidates. If there is no match, the user must deny the connection attempt. The creation of CaS was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}. CaE is designed for scenarios where both devices might not have a display, i.e. pairing between a phone and a keyboard. One device displays the checksum. This checksum is entered into the other device. The first device then compares the entered string and checks for a match.

@@

\subsubsection*{Experimentation methodology comparison}
To further look into the validity of previously discussed results, it is necessary to asses how the respective studies reached these conclusions. Areas for consideration are scheme entropy, attacker strength and participant attributes.

@@

\subsubsection*{Topic conclusion}
Overall, this review has identified several key areas suitable for further work.
The first is the performance assessment of graphical encoding schemes. Recreation of pre-existing results from \cite{hsiao2009study}\cite{tan2017can} is required to corroborate current conclusions and validate results.
Another gap in the research is the consideration into the utilization of encoding schemes in realistic conditions, i.e. ``remove vs. proximity." This topic was initially covered by \cite{shirvanian2017pitfalls} but their scope was limited. Further work, therefore, could increased the scope and touch upon a large number of schemes in these settings.
The final aspect for further work is the limited consideration into the feasibility of attacks on encoding schemes. All of the papers assessed simulated attacks and had minimal consideration for the execution of these attacks. Therefore, further work could delve into the implementation of such attacks and their feasibility in terms of compute and storage complexity.

\subsection{Encoding schemes}
Another area of research is investigations into the actual physical encodings of the hash digest. This section will briefly discuss the current research available on the creation and security of actual encoding schemes. The actual details of the operation of the schemes are outside the scope of this literature review, therefore, minimal attention will be allocated to these details.

@@

\subsubsection*{Pretty Easy Privacy}
\label{sec:pep}
A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}. \pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email or SMS. The imbedded design principles state that above all the systems should be easy to install, use and understand.

@@

\subsubsection*{Topic conclusion}

@@

\subsection{Attacks on encoding schemes}
This area of research studies ways to physically execute attacks on fingerprint encoding schemes. This differs from previously examined work due to papers discussing the performance and fallibility of encoding schemes simulated the attack without consideration for how the attack would be performed. Research in this area is scant, with lots of research attention being directed towards the security of Man-in-the-Middle (MITM) attacks and not the encoding schemes themselves.

@@

\subsubsection*{Topic Conclusion}
Overall the literature for this subtopic remains sparse and incomplete. Further suggested work could look into the feasibility of generating partial collisions for all textual representations alongside quantified effectiveness on users. With the possibility to concentrate on a few selected implementations. The work would aim to focus on the various physical methods used and their feasibility. This is one area the previous literature has failed to cover and has only theoretically quantified attacker strength without consideration for the actual real-world cost of these attacks.
